---
title: "Akhila_Lab1"
author: "Akhila"
date: "4/8/2020"
output: html_document
---

---
title: "Lab1"
author: ""
date: "4/6/2020"
output: html_document
---


```{r Data_structures, include = TRUE}
library(tidyverse)

set.seed(123) # Set random number generation

m <- lm(mpg ~ hp + cyl + drat, mtcars)

l <- list(a = list(m = matrix(1:12, ncol = 3),
                   v = 1:7),
          b = data.frame(student = 1:15,
                         score = rnorm(15, 100, 10)))

```

## From the model results:
### Extract the qr tolerance (tol)
```{r extract_qr_tol, include = TRUE}

m$qr$tol


```

### Extract the term labels from the model  
*Hint:* Use str to inspect the list. This one is tricky and involves pulling an attribute from an attribute.
```{r extract_term_labels, include = TRUE}

terms <- attr(m$model, "terms")
attributes(terms)

attr(terms, "term.labels")
```

## From the list:
### Use at least two different methods to extract m
```{r method_one_extract_m, include = TRUE}
#1
l$a$m

#2
t <- l[["a"]]
t[["m"]]

#3
zoom <- l[["a"]][["m"]]

```

##extract third column of m
```{r method_two_extract_m, include = TRUE}

typeof(zoom)
zoom
#removes structure and re-adds matrix structure
as.matrix(zoom[,3])

#do not drop the structure/dimensions
zoom[,3, drop=FALSE]

```


### Extract the score for student 7
```{r extract_student7_score, include = TRUE}
#method 1
as.data.frame(l[["b"]]) %>% 
filter(student == "7")

#method2
ob <- l[["b"]]
ob[7,2]

```

## Loops  
Use the “airquality” dataset, which is part of base R.

### Split it by Month
```{r split_month, include = TRUE}

airquality
month_split <- split(airquality, airquality$Month)
str(month_split)
```

### Use a for loop to calculate the mean Ozone by month (remember to remove missing data from the calculation)
```{r mean_Ozone, include = TRUE}

d2 <- rep(NA, length(month_split))

for(i in seq_along(d2)) { #pre-determines the number of iterations (d2 = length 5, so 5 iterations)
  d2[i] <- mean(month_split[[i]][["Ozone"]], na.rm = TRUE) #i is already defined, so the mean function runs 5 times through the month_split dataset
}
  
d2 #got to call d2 because we filled it with the means 

  

```

### Replicate this calculation with lapply, sapply, and vapply
```{r replicate_calculation, include = TRUE}

#lapply
l <-lapply(month_split, function(x) mean(x$Ozone, na.rm=TRUE))
str(l)

#sapply simplifies output when possible
s <- sapply(month_split, function(x) mean(x$Ozone, na.rm=TRUE))
str(s) #check out format of output

#vapply requires that we specify output type
v <- vapply(month_split, function(x) mean(x$Ozone, na.rm=TRUE), FUN.VALUE = double(1))
str(v)

```

### Produce separate plots showing the relation between Ozone and Solar.R for each month (with a single loop)
```{r plots_Ozone_Solar}

# t  <- rep(NA, length(month_split))
# titles <- for(i in seq_along(t)) {
#   t[i] <- paste0(month_split[i][["Month"]])
#   }
# t

plots <- lapply(month_split, function(x) {
  ggplot(x, aes(Ozone, Solar.R)) +
    geom_point() +
    geom_smooth() +
    labs(
      title = 
    )
})


```

### Use a for loop to save the plots to a folder on your computer
```{r save_plots, include = TRUE}

dir.create(here::here("akhila_plots"))
filenames <- here::here("akhila_plots",
                        paste0("Month", names(month_split), ".png"))
filenames

for(i in seq_along(plots)) {
  ggsave(filenames[i], 
         plots[[i]],
         device = "png",
         width = 6.5,
         height = 8)
}


```


