---
title: "Akhila_Lab1"
author: "Akhila"
date: "4/8/2020"
output: html_document
---

---
title: "Lab1"
author: ""
date: "4/6/2020"
output: html_document
---


```{r Data_structures, include = TRUE}

set.seed(123) # Set random number generation

m <- lm(mpg ~ hp + cyl + drat, mtcars)

l <- list(a = list(m = matrix(1:12, ncol = 3),
                   v = 1:7),
          b = data.frame(student = 1:15,
                         score = rnorm(15, 100, 10)))

```

## From the model results:
### Extract the qr tolerance (tol)
```{r extract_qr_tol, include = TRUE}

m$qr$tol


```

### Extract the term labels from the model  
*Hint:* Use str to inspect the list. This one is tricky and involves pulling an attribute from an attribute.
```{r extract_term_labels, include = TRUE}

terms <- attr(m$model, "terms")
attributes(terms)

attr(terms, "term.labels")
```

## From the list:
### Use at least two different methods to extract m
```{r method_one_extract_m, include = TRUE}
#1
l$a$m

#2
t <- l[["a"]]
t[["m"]]

#3
zoom <- l[["a"]][["m"]]

```

##extract third column of m
```{r method_two_extract_m, include = TRUE}
typeof(zoom)
zoom
#removes structure and re-adds matrix structure
as.matrix(zoom[,3])

#do not drop the structure/dimensions
zoom[,3, drop=FALSE]

```


### Extract the score for student 7
```{r extract_student7_score, include = TRUE}
#method 1
library(tidyverse)
as.data.frame(l[["b"]]) %>% 
filter(student == "7")

#method2
ob <- l[["b"]]
ob[7,2]

```

## Loops  
Use the “airquality” dataset, which is part of base R.

### Split it by Month
```{r split_month, include = TRUE}

airquality

```

### Use a for loop to calculate the mean Ozone by month (remember to remove missing data from the calculation)
```{r mean_Ozone, include = TRUE}

```

### Replicate this calculation with lapply, sapply, and vapply
```{r replicate_calculation, include = TRUE}

```

### Produce separate plots showing the relation between Ozone and Solar.R for each month (with a single loop)
```{r plots_Ozone_Solar}
#Just Sample Code. NOT Working, YET!
somePlotName <- lapply(by_month, function(x) {
    ggplot(x, aes(Ozone, Solar.R)) +
        geom_point() +
        geom_smooth()
})
```

### Use a for loop to save the plots to a folder on your computer
```{r save_plots, include = TRUE}
#Just Sample Code. NOT Working, YET!
dir.create(here::here("plots"))

solar_ozone <- here::here("plots",
                          paste0("ozone",
                                 names(by_month),
                                 ".png"))
solar_ozone

for(i in seq_along(somePlotName)) {
  ggsave(solar_ozone[i], # single bracket
         somePlotName[[i]], # double bracket
         width = 6.5,
         height = 8)
  }
```