---
title: "Lab1"
author: "Joanna"
date: "4/6/2020"
output: html_document
---

## The purpose of this lab is to get you working with base R looping functions while also being careful about data types.
## Run this code:


```{r Data_structures, include = TRUE}

set.seed(123) # Set random number generation

m <- lm(mpg ~ hp + cyl + drat, mtcars)

l <- list(a = list(m = matrix(1:12, ncol = 3),
                   v = 1:7),
          b = data.frame(student = 1:15,
                         score = rnorm(15, 100, 10)))
```

## From the model results:
### Extract the qr tolerance (tol)
```{r extract_qr_tol, include = TRUE}
# str(m)
m$qr$tol
```

### Extract the term labels from the model  
*Hint:* Use str to inspect the list. This one is tricky and involves pulling an attribute from an attribute.
```{r extract_term_labels, include = TRUE}
str(m$model)

# attributes lists the attributes of an object
# attr extracts attributes out 

# extracting "term" attributes and assigning them as object:
terms <- attr(m$model, "term")

# viewing attributes of "terms":
# attributes(terms)

# extracting "term label" attributes from "terms"
attr(terms, "term.labels")

```

## From the list:
### Use at least two different methods to extract m
```{r method_one_extract_m, include = TRUE}

l$a$m

```

```{r method_two_extract_m, include = TRUE}

t <- l[["a"]]
t[["m"]]

# OR, this works too:

l[["a"]][["m"]]
```

### Extract the third column of m  
Maintain the dimensions (matrix structure).
```{r extract_third_column_m, include = TRUE}

# str(m)
# typeof(m)

m2 <- l[["a"]][["m"]]

# drop=FALSE tells it to maintain dimension structure after doing the subsetting. 
m2[ ,3, drop=FALSE]

```

### Extract the score for student 7
```{r extract_student7_score, include = TRUE}

l2 <- l[["b"]]
l2[7,2]

```

## Loops  
Use the “airquality” dataset, which is part of base R.

### Split it by Month
```{r split_month, include = TRUE}

# airquality
month_split <- split(airquality, airquality$Month)
# str(month_split)

```

### Use a for loop to calculate the mean Ozone by month (remember to remove missing data from the calculation)
```{r mean_Ozone, include = TRUE}

d2 <- rep(NA, length(month_split))
# tells d2 to repeat iterations for the length of month_split(so in this case, 5  times)

for(i in seq_along(d2)) 
  d2[i] <- mean(month_split[[i]][["Ozone"]], na.rm = TRUE) 

# in other words: for every iteration in the sequence (length already defined by  d2), calculate the mean for ozone, removing the NAs

d2 # need to call d2 because we filled it with the means 

```

### Replicate this calculation with lapply, sapply, and vapply
```{r replicate_calculation, include = TRUE}

# lapply
l <-lapply(month_split, function(x) mean(x$Ozone, na.rm=TRUE))
# str(l)

#  sapply simplifies output when possible
s <- sapply(month_split, function(x) mean(x$Ozone, na.rm=TRUE))
# str(s) to check out format of output

# vapply requires that we specify output type, here specified as double
v <- vapply(month_split, function(x) mean(x$Ozone, na.rm=TRUE), FUN.VALUE = double(1))
# str(v) 

```

### Produce separate plots showing the relation between Ozone and Solar.R for each month (with a single loop)
```{r plots_Ozone_Solar, warning=FALSE}

library(tidyverse)

plots <- lapply(month_split, function(x) {
  ggplot(x, aes(Ozone, Solar.R)) +
    geom_point() +
    geom_smooth() +
    labs(
      title = 
    )
})

```

### Use a for loop to save the plots to a folder on your computer
```{r save_plots, include = TRUE, warning=FALSE}

dir.create(here::here("joanna_plots"))
filenames <- here::here("joanna_plots",
                        paste0("Month", names(month_split), ".png"))
filenames

for(i in seq_along(plots)) {
  ggsave(filenames[i], 
         plots[[i]],
         device = "png",
         width = 6.5,
         height = 8)
}

```