---
title: "Lab1"
author: ""
date: "4/6/2020"
output: html_document
---

## The purpose of this lab is to get you working with base R looping functions while also being careful about data types.
## Run this code:
```{r Data_structures, include = TRUE}

set.seed(123) # Set random number generation

m <- lm(mpg ~ hp + cyl + drat, mtcars)

l <- list(a = list(m = matrix(1:12, ncol = 3),
                   v = 1:7),
          b = data.frame(student = 1:15,
                         score = rnorm(15, 100, 10)))
```

## From the model results:
### Extract the qr tolerance (tol)
```{r extract_qr_tol, include = TRUE}
str(m)
m$qr$tol
```

### Extract the term labels from the model  
*Hint:* Use str to inspect the list. This one is tricky and involves pulling an attribute from an attribute.
```{r extract_term_labels, include = TRUE}
str(m$model)
```

## From the list:
### Use at least two different methods to extract m
```{r method_one_extract_m, include = TRUE}

```

```{r method_two_extract_m, include = TRUE}

```

### Extract the third column of m  
Maintain the dimensions (matrix structure).
```{r extract_third_column_m, include = TRUE}

```

### Extract the score for student 7
```{r extract_student7_score, include = TRUE}

```

## Loops  
Use the “airquality” dataset, which is part of base R.

### Split it by Month
```{r split_month, include = TRUE}

```

### Use a for loop to calculate the mean Ozone by month (remember to remove missing data from the calculation)
```{r mean_Ozone, include = TRUE}

```

### Replicate this calculation with lapply, sapply, and vapply
```{r replicate_calculation, include = TRUE}

```

### Produce separate plots showing the relation between Ozone and Solar.R for each month (with a single loop)
```{r plots_Ozone_Solar}
#Just Sample Code. NOT Working, YET!
somePlotName <- lapply(by_month, function(x) {
    ggplot(x, aes(Ozone, Solar.R)) +
        geom_point() +
        geom_smooth()
})
```

### Use a for loop to save the plots to a folder on your computer
```{r save_plots, include = TRUE}
#Just Sample Code. NOT Working, YET!
dir.create(here::here("plots"))

solar_ozone <- here::here("plots",
                          paste0("ozone",
                                 names(by_month),
                                 ".png"))
solar_ozone

for(i in seq_along(somePlotName)) {
  ggsave(solar_ozone[i], # single bracket
         somePlotName[[i]], # double bracket
         width = 6.5,
         height = 8)
  }
```