---
title: "Lab1"
author: ""
date: "4/6/2020"
output: html_document
---

# The purpose of this lab is:  
Get you working with base R looping functions while also being careful about data types.
## Run this code:
```{r Data_structures, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

set.seed(123) # Set random number generation

m <- lm(mpg ~ hp + cyl + drat, mtcars)

l <- list(a = list(m = matrix(1:12, ncol = 3),
                   v = 1:7),
          b = data.frame(student = 1:15,
                         score = rnorm(15, 100, 10)))
```

## From the model results:
### Extract the qr tolerance (tol)
```{r extract_qr_tol}

```

### Extract the term labels from the model  
*Hint:* Use str to inspect the list. This one is tricky and involves pulling an attribute from an attribute.
```{r extract_term_labels}

```

## From the list:
### Use at least two different methods to extract m.
```{r method_one_extract_m}

```

```{r method_two_extract_m}

```

### Extract the third column of m.  
Maintain the dimensions (matrix structure).
```{r extract_third_column_m}

```

### Extract the score for student 7.
```{r extract_student7_score}

```

##Loops
Use the “airquality” dataset, which is part of base R  
### Split it by Month
```{r split_month}

```

### Use a for loop to calculate the mean Ozone by month (remember to remove missing data from the calculation)
```{r mean_Ozone}

```

### Replicate this calculation with lapply, sapply, and vapply
```{r replicate_calculation}

```

### Produce separate plots showing the relation between Ozone and Solar.R for each month (with a single loop).
```{r plots_Ozone_Solar}

```

### Use a for loop to save the plots to a folder on your computer
```{r save_plots}

```

