---
title: "Rowley_Lab1"
author: "Brock Rowley"
date: "4/6/2020"
output: html_document
---

## The purpose of this lab is to get you working with base R looping functions while also being careful about data types.
## Run this code:
```{r Data_structures, include = TRUE}

set.seed(123) # Set random number generation

m <- lm(mpg ~ hp + cyl + drat, mtcars)

l <- list(a = list(m = matrix(1:12, ncol = 3),
                   v = 1:7),
          b = data.frame(student = 1:15,
                         score = rnorm(15, 100, 10)))
```

## From the model results:
### Extract the qr tolerance (tol)
```{r extract_qr_tol, include = TRUE}
tolerance <- m$qr$tol
tolerance
```

### Extract the term labels from the model  
*Hint:* Use str to inspect the list. This one is tricky and involves pulling an attribute from an attribute.
```{r extract_term_labels, include = TRUE}
#str(m)
terms <- attr(m$model, "term")
#attributes(terms)
attr(terms, "term.labels")
#attr(attr(m$model, "term"), "term.labels")
```

## From the list:
### Use at least two different methods to extract m
```{r method_one_extract_m, include = TRUE}
l$a$m
```

```{r method_two_extract_m, include = TRUE}
t <- l[["a"]]
r <- t[["m"]]
r
```

### Extract the third column of m  
Maintain the dimensions (matrix structure).
```{r extract_third_column_m, include = TRUE}
as.matrix(r[ , 3])
```

### Extract the score for student 7
```{r extract_student7_score, include = TRUE}
ob <- l[["b"]]
ob[7,2]

#library(tidyverse)
#as.data.frame(l[["b"]]) %>%
  #filter(student == "7")
```

## Loops  
Use the “airquality” dataset, which is part of base R.

### Split it by Month
```{r split_month, include = TRUE}
data <- split(airquality, airquality$Month)
```

### Use a for loop to calculate the mean Ozone by month (remember to remove missing data from the calculation)
```{r mean_Ozone, include = TRUE}
mean_month <- rep(NA, length(data))
for(i in seq_along(mean_month)) {
  mean_month[i] <- mean(data[[i]][["Ozone"]], na.rm = TRUE)
}
mean_month
```

### Replicate this calculation with lapply, sapply, and vapply
```{r replicate_calculation, include = TRUE}
lapply(data, function(x) mean(x$Ozone, na.rm = TRUE))
sapply(data, function(x) mean(x$Ozone, na.rm = TRUE))
vapply(data, function(x) mean(x$Ozone, na.rm = TRUE), FUN.VALUE = double(1))
```

### Produce separate plots showing the relation between Ozone and Solar.R for each month (with a single loop)
```{r plots_Ozone_Solar, message = FALSE, warning = FALSE}
library(tidyverse)
airquality_p <- lapply(data, function(x) {
    ggplot(x, aes(Ozone, Solar.R)) +
        geom_point() +
        geom_smooth()
})
airquality_p <- lapply(seq_along(airquality_p),
                       function(i) {
                         airquality_p[[i]] +
                           ggtitle(names(airquality_p)[i])
                         })
airquality_p
```

### Use a for loop to save the plots to a folder on your computer
```{r save_plots, include = TRUE, message = FALSE, warning = FALSE}
#dir.create(here::here("brock_plots"))
solar_ozone <- here::here("brock_plots",
                          paste0("ozone",
                                 names(data),
                                 ".png"))
for(i in seq_along(airquality_p)) {
  ggsave(solar_ozone[i],
         airquality_p[[i]],
         width = 6.5,
         height = 8)
  }
```