---
title: "Lab 1 "
author: "Stephanie Gluck"
date: "4/8/2020"
output: html_document
---

## The purpose of this lab is to get you working with base R looping functions while also being careful about data types.

Run this code:
```{r Data_structures, include = TRUE}

set.seed(123) # Set random number generation

m <- lm(mpg ~ hp + cyl + drat, mtcars)

l <- list(a = list(m = matrix(1:12, ncol = 3),
                   v = 1:7),
          b = data.frame(student = 1:15,
                         score = rnorm(15, 100, 10)))
```

## From the model results:
### Extract the qr tolerance (tol)
```{r extract_qr_tol, include = TRUE}

tolerance <- m$qr$tol
tolerance

```

### Extract the term labels from the model  
*Hint:* Use str to inspect the list. This one is tricky and involves pulling an attribute from an attribute.
```{r extract_term_labels, include = TRUE}

str(m)

terms <- attr(m$model, "term")
attributes(terms)
attr(terms, "term.labels")

#alternative method, less clear 
#attr(attr(m$model, "term"), "term.labels")

```

## From the list:
### Use at least two different methods to extract m
```{r extract_m, include = TRUE}

# Method 1
l$a$m

# Method 2 
l[["a"]][["m"]]

```


### Extract the third column of m  
Maintain the dimensions (matrix structure).
```{r extract_third_column_m, include = TRUE}

extract <- l[["a"]][["m"]]

#duse drop = FALSE to not drop the structure/dimensions 
extract[,3, drop = FALSE]

#removes structure and re-adds matrix, not the best way  
#as.matrix(extract[,3])

```

### Extract the score for student 7
```{r extract_student7_score, include = TRUE}

# Method 1
ob <- l[["b"]]
ob
ob[7, 2]

# Method 2
library(tidyverse)
as.data.frame(l[["b"]]) %>% 
  filter(student == 7)

```

## Loops  
Use the “airquality” dataset, which is part of base R.

### Split it by Month
```{r split_month, include = TRUE}

str(airquality)

data <- split(airquality, airquality$Month)
str(data)
attributes(data)

```

### Use a for loop to calculate the mean Ozone by month (remember to remove missing data from the calculation)
```{r mean_Ozone, include = TRUE}

month <- rep(NA, length(data))

for(i in seq_along(month)) {
  month[i] <- mean(data[[i]][["Ozone"]], na.rm = TRUE)
}

month
```

### Replicate this calculation with lapply, sapply, and vapply
```{r replicate_calculation, include = TRUE}

str(data)

lapply(data, function(x) mean(x$Ozone, na.rm = TRUE))

sapply(data, function(x) mean(x$Ozone, na.rm = TRUE))

vapply(data, function(x) mean(x$Ozone, na.rm = TRUE), FUN.VALUE = double(1))

```

### Produce separate plots showing the relation between Ozone and Solar.R for each month (with a single loop)
```{r plots_Ozone_Solar}

airquality_p <- lapply(data, function(x) {
    ggplot(x, aes(Ozone, Solar.R)) +
        geom_point() +
        geom_smooth()
})

# I wanted to add a title to distinguish each plot but was not able to find a way that worked in the previous code so I found a workaround on Stack Overflow.
# https://stackoverflow.com/questions/50041828/pasting-names-of-list-objects-into-a-ggplot-call-during-lapply

airquality_p <- lapply(seq_along(airquality_p), function(i) { 
  airquality_p[[i]] + 
    ggtitle(names(airquality_p)[i])
})

airquality_p

```

### Use a for loop to save the plots to a folder on your computer
```{r save_plots}

dir.create(here::here("stephanie_plots"))

solar_ozone <- here::here("stephanie_plots",
                          paste0("ozone",
                                 names(data),
                                 ".png"))
solar_ozone

for(i in seq_along(airquality_p)) {
  ggsave(solar_ozone[i], # single bracket
         airquality_p[[i]], # double bracket
         width = 6.5,
         height = 8)
  }
```

